A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Quasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3

### 2015-08-21 skeleton.tex
fix to fit guidelines

%\documentclass[12pt,preprint]{aastex}
\documentclass[twocolumn,apj,numberedappendix]{emulateapj}
\usepackage[breaklinks,colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{tleung@astro.cornell.edu}
\newcommand{\Msun}{\mbox{$M_{\odot}$}}
\newcommand{\Rsun}{\mbox{R$_{\odot}$}}
\newcommand{\Lsun}{\mbox{L$_{\odot}$}}
\newcommand{\rarr}{$\rightarrow$}
\newcommand{\CO}{\mbox{CO($J$\,=\,3\,$\rightarrow$\,2) }}
\newcommand{\Lp}{\mbox{$L^{\prime}_\textrm{CO(1-0)}$}}
\newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}}
\newcommand{\eg}{{\sl e.g.,~}}
\newcommand{\ie}{{\sl i.e.,~}}
\newcommand{\pmOne}{\mbox{$^{-1}$}}
\newcommand\tna{\,\tablenotemark{a}}
\newcommand\tnb{\,\tablenotemark{b}}
\newcommand\tnc{\,\tablenotemark{c}}
\newcommand\tnd{\,\tablenotemark{d}}
\newcommand\tne{\,\tablenotemark{e}}
\newcommand\tnf{\,\tablenotemark{f}}
\newcommand\tng{\,\tablenotemark{g}}
\newcommand\tnh{\,\tablenotemark{h}}
\newcommand\tni{\,\tablenotemark{i}}
\newcommand\tnj{\,\tablenotemark{j}}
\newcommand\tnk{\,\tablenotemark{k}}

%\slugcomment{{\sc Accepted to ApJ:} August 1, 2006}
\usepackage{amsmath}
\usepackage{natbib}
\citestyle{aa}
\shorttitle{Study of a strongly-lensed type-2 quasar host SMG at $z$\,=\,2.221}
\shortauthors{Leung \& Riechers}

@@

J0939 ($z$\,=\,2.221) were carried out using CARMA at a redshifted frequency of $\nu_{\rm obs}$\,=\,107.357\,\,GHz (2.79\,\,mm)  (program ID: cf0142; PI: Riechers). The 3\,mm receivers were used to cover the redshifted \CO line and the nearby observed-frame 2.88\,mm continuum emission. The correlator was configured to provide a bandwidth of 3.96 GHz in each sideband, and a spectral resolution of 5.208 MHz ($\sim$\,14.5 km\,\,s\pmOne). 

@@

@@

averaging over all line-free channels, this yields a synthesized clean beam of 12\farcs0\,$\times$\,6\farcs5, $-$55.9$\degr$ east of north, and an rms noise of $\sigma_\textrm{cont}$ = 0.50\,\,mJy\,\,beam\pmOne\ over 7.0 GHz.
%6.968 GHz = (total(1520) - edge * 2 * nwin(16))*5.208 MHz - [linechannel (196 - 153) * (2 * 5.208MHz)]

@@

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{Figure/ContPanel.pdf}
\caption{Left: Contour map of the 104 GHz continuum emission in the foreground radio galaxy 3C220.3.
%The contour levels start at $\pm$2$\sigma$, where $\sigma$ = 0.5 mJy beam\pmOne, and
%increment at steps of $\pm$2$\sigma$.
The beam size is 12\farcs0\,$\times$\,6\farcs5, at P.A.\,=\,
$-$56$\degr$, as indicated in the bottom left corner. Right: CARMA 104 GHz continuum emission (red contours) overlaid on the VLA 9 GHz continuum emission (green contours and grayscale; H14).
The synthesized beam size of the VLA observations is 0$\farcs$6\,$\times$\,0$\farcs$2, at P.A.
76$\degr$. The contour levels of the 104 GHz continuum emission start at $\pm$2$\sigma$, incrementing at steps
of $\pm$2$\sigma$, where $\sigma$ = 0.5 mJy beam\pmOne. The contour levels of the 9 GHz continuum
emission start at $\pm$4$\sigma$, where $\sigma$\,=\,0.064 mJy beam\pmOne, and increment at steps of $\pm$2$^n\sigma$,
where $n$ is a positive integer.
The central cross on each image indicates the position of the radio core of 3C220.3. \label{fig:cont}}
\end{figure*}
%\subsection{New Results: \CO Line Emission}
\subsection{New Results: SMM\,J0939\\ \CO Line Emission}
We detect \CO line emission at $\sim$\,8$\sigma$ significance toward the background SMG SMM\,J0939 at $z$\,=\,2.221.
The lensing-magnified spatial extent of this SMG is $\sim$\,5$\arcsec$, as shown in the Submillimeter Array (SMA) 1\,mm dust continuum image in Figure~\ref{fig:mom0} (H14); as such,
the detected \CO line emission is spatially unresolved. We therefore extract the line profile (Figure~\ref{fig:mom0}) at the peak position of the unresolved
CO emission. Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 21.61\,$\pm$\,2.66\,\,mJy, superimposed on a
continuum level of 4.15\,$\pm$\,0.48~mJy~beam\pmOne, and a line full width at half-maximum (FWHM) of 546\,$\pm$\,36\,\,km\,\,s\pmOne.  \par
We construct a velocity-integrated (0$^\textrm{th}$ moment) map of the \CO line
emission after subtracting continuum emission in the visibility plane. This results in a velocity-integrated \CO line flux of $I_\textrm{CO}$\,=\,12.6\,$\pm$\,2.0 Jy km\,\,s\pmOne\ over a velocity range of $\Delta v$\,$\sim$\,1420 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration
uncertainty. Our \CO line measurement confirms the redshift of SMM\,J0939, yielding $z$\,=\,2.2212\,$\pm$\,0.0010.

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.8\textwidth]{Figure/LinePanel.pdf}
\includegraphics[width=0.65\textwidth]{Figure/smmj0939-co32_spec.eps}
\caption{Top Left: Continuum-subtracted moment-0 map of \CO line emission toward
the background SMG with $\sigma$\,=\,1.03\,Jy\,\,km\,\,s\pmOne\ beam\pmOne\ over a velocity range of $\Delta v$\,$\sim$\,514\,km\,\,s\pmOne. The beam size is 11$\farcs$5\,$\times$\,6\farcs2, at P.A.\,=\,$-$56\degr, as indicated in the bottom left corner.
Top Right: Velocity-integrated \CO line emission (red contours) overlaid on the SMA 1\,mm dust continuum (green contours and grayscale; H14), with an rms noise of $\sigma_\textrm{1\,mm}$\,=\,0.84 mJy beam\pmOne. The beam size of the SMA observations is 1\farcs4$ \times $1\farcs2, P.A. $-$34\degr, as shown
in the bottom left corner.
The central cross on each image corresponds to the same coordinates as in Figure~\ref{fig:cont}. The contour levels 
in both images
start at $\pm$3$\sigma$, incrementing at
steps of $\pm$1$\sigma$.
Bottom:
Spectrum extracted at the peak position of CO line emission, with a spectral resolution of $\Delta v$ $\sim$\,29 km\,\,s\pmOne, and an rms of $\sigma_\textrm{ch}$\,=\,9.5 mJy beam\pmOne\ per channel. The
solid black line shows a Gaussian fit to the \CO line profile, where the velocity scale is relative to $z$\,=\,2.221.
\label{fig:mom0}}
\end{figure*}

@@

The resulting best-fit model as shown in Figure\,\,\ref{fig:lens} shows no significant bowls in the residual
image, and the knots (lensed emission) in the observed SMA data are well-reassembled with the best-fit model.
Our best-fit model yields a magnification
factor of $\mu_\textrm{L}$ = 10.13\,$\pm$\,1.38, this is consistent the value reported by H14 within the errors. All best-fit
parameters are listed in Table~\ref{tab:lensParam}. The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ = 1\farcs22\,$\pm$\,0\farcs01 (8.75 kpc at $z$\,=\,0.685) and $\theta_{E}$ = 0\farcs75\,$\pm$\,0\farcs02 (5.34\,\,kpc at $z$\,=\,0.685), and
the corresponding masses within the Einstein radii are $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(4.86\,$\pm$\,0.08)\,$\times$\,10$^{11}$\,\,\Msun\ and $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(1.82\,$\pm$\,0.07)\,$\times$\,10$^{11}$\,\,\Msun, respectively.
\input{table_lensParams}

@@

Previously,  an upper
limit of $<$ 0.17 mJy at 4.6 GHz has been established by \citet{Mullin06a} on the core component of 3C220.3, and an unambiguous detection of 0.8 mJy at 9 GHz has been reported by H14, suggesting a substantially inverted spectrum of the core (Figure~\ref{fig:SED}).
Consequently, we may naively expect the integrated flux density in our continuum detection of $S_\textrm{104GHz}$\,=\,7.39\,$\pm$\,1.42\,\,mJy to be dominated by the unresolved core component of the foreground FR-II galaxy, which is at $z$\,=\,0.685.
However, the deconvolved spatial size of the source matching that in the resolved image (see Figure~\ref{fig:cont}) is
suggestive of a marginally resolved detection of the extended lobe components with non-negligible emission.
This is plausible given that the orientation of the synthesized beam in our observations is in alignment with the
axis along the
lobes of the radio galaxy, as shown in Figure~\ref{fig:cont}. We investigate this disparity by fitting models to
existing SED measurements as listed in Table \ref{tab:SEDdataRadio}, and extrapolating the fit to
estimate the flux density of the lobes at the frequency of our continuum measurement.
\input{table_SED}
Following Equation (1) in \citet{Cleary07a}, the fit to the lobe emission can be expressed as a parabolic function:
\begin{equation}
\log F_{\nu}^{\mathrm lobe} (\nu) \propto - \beta\ (\log\ \nu - \log \nu_{t})^2  + \log (\exp({\frac{\nu}{\nu_c^{\mathrm lobe}}}))
\end{equation}
where $F_{\nu}^{\mathrm lobe}$ is the flux density of the lobes, $\beta$ is a parameter representing the bending
of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches
unity, and $\nu_c^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy
distribution. 
The extrapolated flux density at 104\,\,GHz is consistent with the peak flux density of our continuum
measurement (Figure~\ref{fig:SED}). The 9$\sigma$ detection of the continuum thereby suggests a
dominant contribution from the lobes, and that the peak flux density does not correspond to emission toward
the core. Moreover, the peak position of the 104\,\,GHz continuum is
centered toward the northern lobe (Figure~\ref{fig:cont}), which further supports our argument. 
Consequently, a conservative upper limit of $S_\nu$\,$<$\,4.93 mJy on the core emission can be established using the measured peak flux density. Yet, by considering the 
difference between the integrated flux density from our measurement and the flux density from an extrapolation of the model (see Figure~\ref{fig:SED}; $S_\textrm{104GHz, fit}$~=~5.10 mJy), we establish a more stringent constrain on this upper limit of $S_\nu$\,$<$\,2.29 mJy. We did not 
 extrapolate the core measurements to the frequency of our continuum, as previous measurements of the core are 
 taken 
 across different epochs. 
\par
Studies by \citet{Meisenheimer89a} and \citet{Hardcastle08a} have suggested that spectra of hotspots are flat up to optical frequencies, where some exhibit spectral steepening in cm and mm wavelengths (\eg 3C123). At the resolution of our observations, it is unclear whether the measured flux density is dominated by emission from the compact hotspot or that from the surrounding diffuse lobe components.

\begin{figure}[!tbph]
\centering
\includegraphics[width=0.5\textwidth]{Figure/3C220_3_FullSED2.pdf}
\caption{The SEDs of 3C220.3 (solid purple line) and SMM\,J0939 (dashed purple line and solid cyan line) including the new measurements presented in this paper.
The solid purple line corresponds to the parabolic function we
fit to the existing data associated with 3C220.3 (black dots; see Table \ref{tab:SEDdataRadio}).
The red dots at 104 GHz correspond to
our continuum measurements (integrated, peak, and difference, respectively).
The dashed purple line and
the solid cyan line correspond to the best-fit optically thick and optically thin models of SMM\,J0939, respectively, using the photometric data from H14. \label{fig:SED}}
\end{figure}

@@

\input{table_mbb}
The best-fit values in both regimes are listed in Table \ref{tab:mbb}, and the correlation plots are available in the Appendix. The best-fit solution of an optically thin
model corresponds to $\chi^2$ = 5.31 with 3 degrees of freedom, whereas that of an optically thick model
corresponds to $\chi^2$ = 2.25 with 2 degrees of freedom, suggesting a better fit than in the optically thin
case. In the subsequent analysis, we employ the inferred values from the optically thick model.
The best-fit solution yields a FIR luminosity (rest-frame 42.5$-$122.5\micron) of $L_\textrm{FIR}$ = 53.3$^{+1.1}_{-1.1}$\,$\times$\,10$^{12}$\,\Lsun, and a total infrared (IR; rest-frame 8$-$1000 \micron) luminosity of $L_\textrm{IR}$ = 88.5$^{+2.6}_{-2.6}$\,$\times$\,10$
^{12}$\,\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64\,\,m$^2$\,\,kg\pmOne\ at 125.0\,\,$
\micron$ \citep{Dunne03a}, we derive the dust mass using the following expression:
\begin{equation}
M_\textrm{dust}\,=\,S_{\nu} D_{L}^2 [(1 + z) \kappa_{\nu} B_{\nu}]^{-1} \tau_{\nu} [1-
\exp(-\tau_{\nu})]^{-1}
\end{equation}
where $S_{\nu}$ is the flux density in erg\,s\pmOne\,cm$^{-2}$\,Hz\pmOne, $D_\textrm{L}$ is the luminosity distance in cm, $\kappa_{\nu}$ is the dust
absorption coefficient in cm$^2$\,g\pmOne, $\tau_{\nu}$ is the optical depth, and $B_{\nu}$ is the Planck function in units of erg\,s\pmOne\,cm$^{-2}$\,Hz\pmOne\,sr\pmOne;
all quantities are expressed in the observed-frame. We find a dust mass of $M_\textrm{dust}$ = 50.5$^{20.4}_{-20.2}\times$10$^8$\,\,\Msun, the uncertainties do not include those in the dust absorption coefficient ($\kappa_{\nu}$). These properties are derived based on the SED fitting to the photometric data, \ie prior
to lensing correction.

@@

\section{Discussion And Conclusions}
\input{table_compareSMG}
We present the detection of \CO line emission toward SMM\,J0939+8315, a strongly-lensed SMG that is hosting a type-2 quasar, refining the redshift
to $z$\,=\,2.2212\,$\pm$\,0.0010. The underlying continuum is detected at $\sim$\,9$\sigma$ significance, where the flux density is likely dominated by emission from the lobes and hotspot of the foreground radio galaxy 3C220.3.

@@

\acknowledgments
We thank Shane Bussmann for providing the code {\sc uvmcmcfit} for lens modeling, sharing the SMA and VLA data, and for helpful discussions; Alex Conley for providing the code {\sc mbb\_emcee} for SED fitting. 
%We acknowledge the WENSS team for providing the radio measurements for 3C220.3.
Support for CARMA construction was derived from the
Gordon and Betty Moore Foundation, the Kenneth T. and Eileen
L. Norris Foundation, the James S. McDonnell Foundation, the
Associates of the California Institute of Technology, the University
of Chicago, the states of Illinois, California, and Maryland,
and the National Science Foundation. 
Ongoing CARMA development
and operations are supported by the National Science
Foundation under a cooperative agreement, and by the CARMA
consortium universities.
%Facilities: \facility{CARMA}
\newpage
\bibliographystyle{apj}
\bibliography{J0939}

>>>>

% submission prep
% what does this mean
% Multiplication
% Explicit multiplication signs (dots or crosses), except for scientific notation, grids, vector operators, and when a multiplication wraps to a following line, are omitted.
% online said;: should go in alphabetical order, so should I do Ivison 11 before R11?
%\documentclass[12pt,preprint]{aastex}
\documentclass[twocolumn,apj,numberedappendix]{emulateapj}
\usepackage[breaklinks,colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{tleung@astro.cornell.edu}
\newcommand{\Msun}{\mbox{$M_{\odot}$}}
\newcommand{\Rsun}{\mbox{R$_{\odot}$}}
\newcommand{\Lsun}{\mbox{L$_{\odot}$}}
\newcommand{\rarr}{$\rightarrow$}
\newcommand{\CO}{\mbox{CO($J$\,=\,3\,$\rightarrow$\,2) }}
\newcommand{\Lp}{\mbox{$L^{\prime}_\textrm{CO(1-0)}$}}
\newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}}
\newcommand{\eg}{{\sl e.g.,~}}
\newcommand{\ie}{{\sl i.e.,~}}
\newcommand{\pmOne}{\mbox{$^{-1}$}}
\newcommand\tna{\,\tablenotemark{a}}
\newcommand\tnb{\,\tablenotemark{b}}
\newcommand\tnc{\,\tablenotemark{c}}
\newcommand\tnd{\,\tablenotemark{d}}
\newcommand\tne{\,\tablenotemark{e}}
\newcommand\tnf{\,\tablenotemark{f}}
\newcommand\tng{\,\tablenotemark{g}}
\newcommand\tnh{\,\tablenotemark{h}}
\newcommand\tni{\,\tablenotemark{i}}
\newcommand\tnj{\,\tablenotemark{j}}
\newcommand\tnk{\,\tablenotemark{k}}

%\slugcomment{{\sc Accepted to ApJ:} August 1, 2006}
\slugcomment{To be submitted to the ApJ}
\usepackage{amsmath}
\usepackage{natbib}
\citestyle{aa}
\shorttitle{Study of a strongly-lensed type-2 quasar host SMG at $z$\,=\,2.221}
\shortauthors{Leung \& Riechers}

@@

J0939 ($z$\,=\,2.221) were carried out using CARMA at a redshifted frequency of $\nu_{\rm obs}$\,=\,107.357\,\,GHz (2.79\,\,mm)  (program ID: cf0142; PI: Riechers). The 3\,mm receivers were used to cover the redshifted \CO line and the nearby observed-frame 2.88\,mm continuum emission. The correlator was configured to provide an effective bandwidth of 3.708 GHz in each sideband, and a spectral resolution of 5.208 MHz ($\sim$\,14.5 km\,\,s\pmOne). 

@@

% DR said take out edge channels, since the subbands overlap, and the usable bandwidth is 8 * (95 - 6) * 5.208 

@@

averaging over all line-free channels, this yields a synthesized clean beam of 12\farcs0\,$\times$\,6\farcs5, $-$55.9$\degr$ east of north, and an rms noise of $\sigma_\textrm{cont}$ = 0.50\,\,mJy\,\,beam\pmOne\ over 6.8 GHz.
%7416.192 MHz = (total(1520) - edge * 2 * nwin(16))*5.208 MHz 
%7416.192 - [FWZI linechannel (55) * (2 * 5.208MHz)] = 6843.312

@@

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{Figure/ContPanel_cmyk.eps}
\caption{Left: Contour map of the 104 GHz continuum emission in the foreground radio galaxy 3C220.3.
%The contour levels start at $\pm$2$\sigma$, where $\sigma$ = 0.5 mJy beam\pmOne, and
%increment at steps of $\pm$2$\sigma$.
The beam size is 12\farcs0\,$\times$\,6\farcs5, at P.A.\,=\,
$-$56$\degr$, as indicated in the bottom left corner. Right: CARMA 104 GHz continuum emission (red contours) overlaid on the VLA 9 GHz continuum emission (green contours and grayscale; H14).
The synthesized beam size of the VLA observations is 0$\farcs$6\,$\times$\,0$\farcs$2, at P.A.
76$\degr$. The contour levels of the 104 GHz continuum emission start at $\pm$2$\sigma$, incrementing at steps
of $\pm$2$\sigma$, where $\sigma$ = 0.5 mJy beam\pmOne. The contour levels of the 9 GHz continuum
emission start at $\pm$4$\sigma$, where $\sigma$\,=\,0.064 mJy beam\pmOne, and increment at steps of $\pm$2$^n\sigma$,
where $n$ is a positive integer.
The central cross on each image indicates the position of the radio core of 3C220.3. \label{fig:cont}}
\end{figure*}
%\subsection{New Results: \CO Line Emission}
\subsection{New Results: SMM\,J0939\\ \CO Line Emission}
We detect \CO line emission at $\sim$\,8$\sigma$ significance toward the background SMG SMM\,J0939 at $z$\,=\,2.221.
The lensing-magnified spatial extent of this SMG is $\sim$\,5$\arcsec$, as shown in the Submillimeter Array (SMA) 1\,mm dust continuum image in Figure~\ref{fig:mom0} (H14); as such,
the detected \CO line emission is spatially unresolved. We therefore extract the line profile (Figure~\ref{fig:mom0}) at the peak position of the unresolved
CO emission. Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 21.61\,$\pm$\,2.66\,\,mJy, superimposed on a
continuum level of 4.15\,$\pm$\,0.48~mJy~beam\pmOne, and a line full width at half-maximum (FWHM) of 546\,$\pm$\,36\,\,km\,\,s\pmOne.  \par
We construct a velocity-integrated (0$^\textrm{th}$ moment) map of the \CO line
emission after subtracting continuum emission in the visibility plane. This results in a velocity-integrated \CO line flux of $I_\textrm{CO}$\,=\,12.6\,$\pm$\,2.0 Jy km\,\,s\pmOne\ over a velocity range of $\Delta v$\,$\sim$\,1420 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration
uncertainty. Our \CO line measurement confirms the redshift of SMM\,J0939, yielding $z$\,=\,2.2212\,$\pm$\,0.0010.

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.8\textwidth]{Figure/LinePanel_cmyk.eps}
\includegraphics[width=0.65\textwidth]{Figure/smmj0939-co32_spec.eps}
\caption{Top Left: Continuum-subtracted moment-0 map of \CO line emission toward
the background SMG with $\sigma$\,=\,1.03\,Jy\,\,km\,\,s\pmOne\ beam\pmOne\ over a velocity range of $\Delta v$\,$\sim$\,514\,km\,\,s\pmOne. The beam size is 11$\farcs$5\,$\times$\,6\farcs2, at P.A.\,=\,$-$56\degr, as indicated in the bottom left corner.
Top Right: Velocity-integrated \CO line emission (red contours) overlaid on the SMA 1\,mm dust continuum (green contours and grayscale; H14), with an rms noise of $\sigma_\textrm{1\,mm}$\,=\,0.84 mJy beam\pmOne. The beam size of the SMA observations is 1\farcs4$ \times $1\farcs2, P.A. $-$34\degr, as shown
in the bottom left corner.
The central cross on each image corresponds to the same coordinates as in Figure~\ref{fig:cont}. The contour levels 
in both images
start at $\pm$3$\sigma$, incrementing at
steps of $\pm$1$\sigma$.
Bottom:
Spectrum extracted at the peak position of CO line emission, with a spectral resolution of $\Delta v$ $\sim$\,29 km\,\,s\pmOne, and an rms of $\sigma_\textrm{ch}$\,=\,9.5 mJy beam\pmOne\ per channel. The
solid black line shows a Gaussian fit to the \CO line profile, where the velocity scale is relative to $z$\,=\,2.221.
\label{fig:mom0}}
\end{figure*}

@@

The resulting best-fit model as shown in Figure\,\,\ref{fig:lens} shows no significant bowls in the residual
image, and the knots (lensed emission) in the observed SMA data are well-reassembled with the best-fit model.
Our best-fit model yields a magnification
factor of $\mu_\textrm{L}$ = 10.13\,$\pm$\,1.38, this is consistent the value reported by H14 within the errors. All best-fit
parameters are listed in Table~\ref{tab:lensParam}. The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ = 1\farcs22\,$\pm$\,0\farcs01 (8.75 kpc at $z$\,=\,0.685) and $\theta_{E}$ = 0\farcs75\,$\pm$\,0\farcs02 (5.34\,\,kpc at $z$\,=\,0.685), and
the corresponding masses within the Einstein radii are $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(4.86\,$\pm$\,0.08)\,$\times$\,10$^{11}$\,\,\Msun\ and $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(1.82\,$\pm$\,0.07)\,$\times$\,10$^{11}$\,\,\Msun, respectively.
%\input{table_lensParams}

@@

Previously,  an upper
limit of $<$ 0.17 mJy at 4.6 GHz has been established by \citet{Mullin06a} on the core component of 3C220.3, and an unambiguous detection of 0.8 mJy at 9 GHz has been reported by H14, suggesting a substantially inverted spectrum of the core (Figure~\ref{fig:SED}).
Consequently, we may naively expect the integrated flux density in our continuum detection of $S_\textrm{104GHz}$\,=\,7.39\,$\pm$\,1.42\,\,mJy to be dominated by the unresolved core component of the foreground FR-II galaxy, which is at $z$\,=\,0.685.
However, the deconvolved spatial size of the source matching that in the resolved image (see Figure~\ref{fig:cont}) is
suggestive of a marginally resolved detection of the extended lobe components with non-negligible emission.
This is plausible given that the orientation of the synthesized beam in our observations is in alignment with the
axis along the
lobes of the radio galaxy, as shown in Figure~\ref{fig:cont}. We investigate this disparity by fitting models to
existing SED measurements as listed in Table \ref{tab:SEDdataRadio}, and extrapolating the fit to
estimate the flux density of the lobes at the frequency of our continuum measurement.
%\input{table_SED}
Following Equation (1) in \citet{Cleary07a}, the fit to the lobe emission can be expressed as a parabolic function:
\begin{equation}
\log F_{\nu}^{\mathrm lobe} (\nu) \propto - \beta\ (\log\ \nu - \log \nu_{t})^2  + \log (\exp({\frac{\nu}{\nu_c^{\mathrm lobe}}}))
\end{equation}
where $F_{\nu}^{\mathrm lobe}$ is the flux density of the lobes, $\beta$ is a parameter representing the bending
of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches
unity, and $\nu_c^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy
distribution. 
The extrapolated flux density at 104\,\,GHz is consistent with the peak flux density of our continuum
measurement (Figure~\ref{fig:SED}). The 9$\sigma$ detection of the continuum thereby suggests a
dominant contribution from the lobes, and that the peak flux density does not correspond to emission toward
the core. Moreover, the peak position of the 104\,\,GHz continuum is
centered toward the northern lobe (Figure~\ref{fig:cont}), which further supports our argument. 
Consequently, a conservative upper limit of $S_\nu$\,$<$\,4.93 mJy on the core emission can be established using the measured peak flux density. Yet, by considering the 
difference between the integrated flux density from our measurement and the flux density from an extrapolation of the model (see Figure~\ref{fig:SED}; $S_\textrm{104GHz, fit}$~=~5.10 mJy), we establish a more stringent constrain on this upper limit of $S_\nu$\,$<$\,2.29 mJy. We did not 
 extrapolate the core measurements to the frequency of our continuum, as previous measurements of the core are 
 taken 
 across different epochs. 
\par
Studies by \citet{Meisenheimer89a} and \citet{Hardcastle08a} have suggested that spectra of hotspots are flat up to optical frequencies, where some exhibit spectral steepening in cm and mm wavelengths (\eg 3C123). At the resolution of our observations, it is unclear whether the measured flux density is dominated by emission from the compact hotspot or that from the surrounding diffuse lobe components.

\begin{figure}[!tbph]
\centering
\includegraphics[width=0.5\textwidth]{Figure/3C220_3_FullSED2.pdf}
\caption{SEDs of 3C220.3 (solid purple line) and SMM\,J0939 (dashed purple line and solid cyan line) including the new measurements presented in this paper.
The solid purple line corresponds to the parabolic function we
fit to the existing data associated with 3C220.3 (black dots; see Table \ref{tab:SEDdataRadio}).
The red dots at 104 GHz correspond to
our continuum measurements (integrated, peak, and difference, respectively).
The dashed purple line and
the solid cyan line correspond to the best-fit optically thick and optically thin models of SMM\,J0939, respectively, using the photometric data from H14. \label{fig:SED}}
\end{figure}

@@

%\input{table_mbb}
The best-fit values in both regimes are listed in Table \ref{tab:mbb}, and the correlation plots are available in the Appendix. The best-fit solution of an optically thin
model corresponds to $\chi^2$ = 5.31 with 3 degrees of freedom, whereas that of an optically thick model
corresponds to $\chi^2$ = 2.25 with 2 degrees of freedom, suggesting a better fit than in the optically thin
case. In the subsequent analysis, we employ the inferred values from the optically thick model.
The best-fit solution yields a FIR luminosity (rest-frame 42.5$-$122.5\micron) of $L_\textrm{FIR}$ = 53.3$^{+1.1}_{-1.1}$\,$\times$\,10$^{12}$\,\Lsun, and a total infrared (IR; rest-frame 8$-$1000 \micron) luminosity of $L_\textrm{IR}$ = 88.5$^{+2.6}_{-2.6}$\,$\times$\,10$
^{12}$\,\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64\,\,m$^2$\,\,kg\pmOne\ at 125.0\,\,$
\micron$ \citep{Dunne03a}, we derive the dust mass using the following expression:
\begin{equation}
M_\textrm{dust}\,=\,S_{\nu} D_{L}^2 [(1 + z) \kappa_{\nu} B_{\nu}]^{-1} \tau_{\nu} [1-
\exp(-\tau_{\nu})]^{-1}
\end{equation}
where $S_{\nu}$ is the flux density in erg\,s\pmOne\,cm$^{-2}$\,Hz\pmOne, $D_\textrm{L}$ is the luminosity distance in cm, $\kappa_{\nu}$ is the dust
absorption coefficient in cm$^2$\,g\pmOne, $\tau_{\nu}$ is the optical depth, and $B_{\nu}$ is the Planck function in units of erg\,s\pmOne\,cm$^{-2}$\,Hz\pmOne\,sr\pmOne;
all quantities are expressed in the observed-frame. We find a dust mass of $M_\textrm{dust}$ = 50.5$^{20.4}_{-20.2}\times$10$^8$\,\,\Msun, the uncertainties do not include those in the dust absorption coefficient ($\kappa_{\nu}$). These properties are derived based on the SED fitting to the photometric data, \ie prior
to lensing correction.

@@

\section{Discussion And Conclusions}
%\input{table_compareSMG}
We present the detection of \CO line emission toward SMM\,J0939+8315, a strongly-lensed SMG that is hosting a type-2 quasar, refining the redshift
to $z$\,=\,2.2212\,$\pm$\,0.0010. The underlying continuum is detected at $\sim$\,9$\sigma$ significance, where the flux density is likely dominated by emission from the lobes and hotspot of the foreground radio galaxy 3C220.3.

@@

\acknowledgments
We thank Shane Bussmann for providing the code {\sc uvmcmcfit} for lens modeling, sharing the SMA and VLA data, and for helpful discussions; Alex Conley for providing the code {\sc mbb\_emcee} for SED fitting. 
%We acknowledge the WENSS team for providing the radio measurements for 3C220.3.
Support for CARMA construction was derived from the
Gordon and Betty Moore Foundation, the Kenneth T. and Eileen
L. Norris Foundation, the James S. McDonnell Foundation, the
Associates of the California Institute of Technology, the University
of Chicago, the states of Illinois, California, and Maryland,
and the National Science Foundation. 
Ongoing CARMA development
and operations are supported by the National Science
Foundation under a cooperative agreement, and by the CARMA
consortium universities.
%Facilities: \facility{CARMA}
\newpage
\bibliographystyle{apj}
%\bibliography{J0939}
\begin{thebibliography}{}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{{Baldwin} {et~al.}(1985){Baldwin}, {Boysen}, {Hales}, {Jennings},
  {Waggett}, {Warner}, \& {Wilson}}]{r2728}
{Baldwin}, J.~E., {Boysen}, R.~C., {Hales}, S.~E.~G., {et~al.} 1985, \mnras,
  217, 717

\bibitem[{{Begelman} {et~al.}(1984){Begelman}, {Blandford}, \&
  {Rees}}]{Begelman84a}
{Begelman}, M.~C., {Blandford}, R.~D., \& {Rees}, M.~J. 1984, Reviews of Modern
  Physics, 56, 255

\bibitem[{{Blain} {et~al.}(2002){Blain}, {Smail}, {Ivison}, {Kneib}, \&
  {Frayer}}]{blain02a}
{Blain}, A.~W., {Smail}, I., {Ivison}, R.~J., {Kneib}, J.-P., \& {Frayer},
  D.~T. 2002, \physrep, 369, 111

\bibitem[{{Bothwell} {et~al.}(2013){Bothwell}, {Smail}, {Chapman}, {Genzel},
  {Ivison}, {Tacconi}, {Alaghband-Zadeh}, {Bertoldi}, {Blain}, {Casey}, {Cox},
  {Greve}, {Lutz}, {Neri}, {Omont}, \& {Swinbank}}]{Bothwell13a}
{Bothwell}, M.~S., {Smail}, I., {Chapman}, S.~C., {et~al.} 2013, \mnras, 429,
  3047

\bibitem[{{Bouch{\'e}} {et~al.}(2007){Bouch{\'e}}, {Cresci}, {Davies},
  {Eisenhauer}, {F{\"o}rster Schreiber}, {Genzel}, {Gillessen}, {Lehnert},
  {Lutz}, {Nesvadba}, {Shapiro}, {Sternberg}, {Tacconi}, {Verma}, {Cimatti},
  {Daddi}, {Renzini}, {Erb}, {Shapley}, \& {Steidel}}]{B07a}
{Bouch{\'e}}, N., {Cresci}, G., {Davies}, R., {et~al.} 2007, \apj, 671, 303

\bibitem[{{Bussmann} {et~al.}(2015){Bussmann}, {Riechers}, {Fialkov},
  {Scudder}, {Hayward}, {Cowley}, {Bock}, {Calanog}, {Chapman}, {Cooray}, {De
  Bernardis}, {Farrah}, {Fu}, {Gavazzi}, {Hopwood}, {Ivison}, {Jarvis},
  {Lacey}, {Loeb}, {Oliver}, {Perez-Fournon}, {Rigopoulou}, {Roseboom},
  {Scott}, {Smith}, {Vieira}, {Wang}, \& {Wardlow}}]{Bussmann15a}
{Bussmann}, R.~S., {Riechers}, D., {Fialkov}, A., {et~al.} 2015, ArXiv
  e-prints, arXiv:1504.05256

\bibitem[{{Carilli} \& {Walter}(2013)}]{Carilli13a}
{Carilli}, C.~L., \& {Walter}, F. 2013, \araa, 51, 105
